Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-19 awipev-CO2.Rmd
added chunk Zeppelin CO2 data

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
  dplyr::rename(pressure = pressure_insitu_ctd,
                s_insitu = sal_insitu_ctd,
                s_fb = sal_fb, 
                s_mix = sal_mix,
                t_11m = temp_insitu_11m,
                t_insitu = temp_insitu_ctd, 
                t_fb = temp_fb, 
                t_sf = temp_sf, 
                t_dur = temp_dur, 
                at = at, 
                at_calc =at_calc,
                ct = ct, 
                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
                ph_s_dur_t_fb = ph_s_dur_temp_fb,
                pco2 = pco2_corr,
                pco2_calc = pco2_calc_fb,
                pH_sf = pHint_tot_sf,
                ph_dur = ph_dur_corr
                )
saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity in FerryBox 
# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
# t_11m = temperature in situ at 11 m
# t_insitu = temperature in situ (profiler), 
# t_fb = temperature in FerryBox 
# t_sf = temperature SeaFET (profiler), °C
# t_dur = temperature Durafet (FerryBox)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
# pco2 = pCO2 in Ferrybox
# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
# pH_sf = pH SeaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
```

>>>>

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
  dplyr::rename(pressure = pressure_insitu_ctd,
                s_insitu = sal_insitu_ctd,
                s_fb = sal_fb, 
                s_mix = sal_mix,
                t_11m = temp_insitu_11m,
                t_insitu = temp_insitu_ctd, 
                t_fb = temp_fb, 
                t_sf = temp_sf, 
                t_dur = temp_dur, 
                at = at, 
                at_calc =at_calc,
                ct = ct, 
                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
                ph_s_dur_t_fb = ph_s_dur_temp_fb,
                pco2 = pco2_corr,
                pco2_calc = pco2_calc_fb,
                pH_sf = pHint_tot_sf,
                ph_dur = ph_dur_corr
                )
saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity in FerryBox 
# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
# t_11m = temperature in situ at 11 m
# t_insitu = temperature in situ (profiler), 
# t_fb = temperature in FerryBox 
# t_sf = temperature SeaFET (profiler), °C
# t_dur = temperature Durafet (FerryBox)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
# pco2 = pCO2 in Ferrybox
# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
# pH_sf = pH SeaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
```
```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2 <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  skip = 181,
  col_names = TRUE,
  na = "-999.999",
  ) %>%
  dplyr::mutate(co2 = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))
  ) %>%
  dplyr::select(datetime, co2)
p_atm_co2 <- ggplot(data=atm_co2) +
  geom_point(aes(x = datetime, y = co2), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
```
